The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
L628

A fourth method, which we do not consider due to its high cost, would be to run full hydrodynamic simulations of the disk. Such simulations would account for all the additional effects discussed in Section \ref{sec:discussion}, but are not suitable for a large parameter space study. In a detailed study of a particular system our results can be used to gain insight into the dynamics before simulating the full disk. For example, equation (\ref{eq:j-full-disk}) can be used to compute $j$ for a power-law disk, and any of the methods described in Section \ref{sec:analytic}-\ref{sec:reb} can then be used to estimate the dynamical state of the system.

>>>>

A fourth method, which we do not consider due to its high cost, would be to run full hydrodynamic simulations of the disk. Such simulations would account for all the additional effects discussed in Section \ref{sec:discussion}, but are not suitable for a large parameter space study. In a detailed study of a particular system our results can be used to gain insight into the dynamics before simulating the full disk. For example, equation (\ref{eq:j-full-disk}) can be used to compute $j$ for a power-law disk, and any of the methods described in Sections \ref{sec:analytic}-\ref{sec:reb} can then be used to estimate the dynamical state of the system.
